GPU Acceleration of the Material Point Method

### 2019-02-07 pres/pres.tex
video embedded

\documentclass{beamer}
\usepackage{listings}
\usepackage{xurl}
\urlstyle{sf}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{color}
\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage[english,ngerman]{babel}
\usepackage[backend=biber,style=alphabetic]{biblatex}
\usepackage{mathtools}
\usepackage{subdepth}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{svg}
\usepackage{xcolor,colortbl}

@@

\begin{document}
\begin{frame}
  \begin{enumerate}
    \item \cite{MPM:COURSE}
  \end{enumerate}
\end{frame}
\selectlanguage{english}
\printbibliography
\end{document}

>>>>

\documentclass{beamer}
\usetheme{Malmoe}
\usecolortheme{seahorse}
\usepackage{csquotes}
\usepackage{listings}
\usepackage{xurl}
\urlstyle{sf}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{color}
\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage[english,ngerman]{babel}
\usepackage[backend=biber,style=alphabetic]{biblatex}
\usepackage{mathtools}
\usepackage{subdepth}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{svg}
\usepackage{xcolor,colortbl}
\usepackage{media9}
\usepackage[font=Times,
timeinterval=30,
timeduration=20,
timewarningfirst=75,
timewarningsecond=90,
colorwarningfirst=blue,
colorwarningsecond=red]{tdclock}
\setbeamertemplate{footline}{%
    \hspace*{2ex}%
    \scriptsize{%
        \cronominutes~-~\tdhours\hspace{0.1ex}:\hspace*{0.5ex}\tdminutes%
    }%
    \hfill\insertframenumber/\inserttotalframenumber
    \hspace*{2ex}%
}

@@

%Information to be included in the title page:

\title{GPU Acceleration of the Material Point Method}

\author % (optional, for multiple authors)
{Fabian Meyer}

\institute % (optional)
{University of Koblenz}

\date{Kolloquium Computergrafik, 14 February 2019}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\section{Motivation on a GPU MPM Approach}

\subsection{a}
\begin{minipage}{.4\pdfpagewidth}
\begin{frame}
\includemedia[
  width=160,
  height=90,
  activate=pageopen,
  addresource=snowh264.mp4,
  flashvars={source=snowh264.mp4&autoPlay=true&loop=true&repeat=always}
  ]{\includegraphics{snow.jpg}}{VPlayer.swf}
Videoi
\end{minipage}
\end{frame}

\section{A Gentle Introduction to the MPM}

\subsection{b}

\begin{frame}
\frametitle{hi}
  \begin{enumerate}
    \item \cite{MPM:COURSE}
  \end{enumerate}
\end{frame}

\section{A MPM Guide on GPGPU Pitfalls and Optimizations}

\subsection{c}

\begin{frame}
\frametitle{hi}
  \begin{enumerate}
    \item \cite{MPM:COURSE}
  \end{enumerate}
\end{frame}

\section{Delving Deeper: Further Opportunities}

\subsection{d}

\begin{frame}
\frametitle{hi}
  \begin{enumerate}
    \item \cite{MPM:COURSE}
  \end{enumerate}
\end{frame}

\selectlanguage{english}
\printbibliography
\end{document}
